---
title: "Introduction to ResNatSeed"
author: "Marco Pittarello and Davide Barberis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_ResNatSeed}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ResNatSeed)
```

## What it does

*ResNatSeed* is an R package that compute the suitability of a certain seed mixture with a site where the seeds would be sown for restoration purposes in a degraded site.

## Important key words

**restoration site**: degraded site that needs to be restored through sowing

**donor grassland**: grassland in which plant material is harvested (e.g. through brushing) to provide native seeds to restoration sites

**vegetation and topographical variables database**: dataframe containing the composition of a set of vegetation surveys and their corresponding topographic variables (elevation, slope and aspect)

**training database**: dataframe with the species eligible for the statistical modelling, selected on the basis of their frequency and abundance in the **vegetation and topographical variables database**. Each species is associated with the values of topographic variables (elevation, slope and aspect) and its abundance.

**species codes - CEP names**: an eight-letter abbreviation of species names according to the Cornell Ecology Programs (CEP). **[vegan]{make.cepnames}**

**seed mixture and donor grassland composition**: The 'seed mixture' is the list of the species and their abundance in the seed batch. The 'donor grassland composition' is the list of the species and their abundance surveyed in a grassland where native seeds are harvested.

**topographical variables of the restoration site**: values of the elevation, slope, and aspect of a degraded site that needs to be restored through sowing.

**Suitability Index (SI)**: suitability of a seed mixture or donor grassland to restore a site with specific topographic characteristics. It ranges between 0 and 1. When SI=0 the restoration site is totally beyond the optimal ecological ranges of all species of the seed mixture or donor grassland, which is therefore not appropriate for the site restoration. Conversely, when SI=1 the restoration site has the optimal ecological conditions for all species of the seed mixture or donor grassland, which is therefore perfectly appropriate for the site restoration.

**Reliability Index (RI)**: index of the reliability of the Suitability Index (SI). The RI ranges between 0 and 1. When RI is close to 0 it means that few to none species contribute to the computation of the SI, whereas when RI is close to 1 the SI is computed with most to all species. Therefore, the higher is the RI, the most reliable is the SI. Not all the species of the seed mixture and donor grassland composition may modeled as i) they can be missing from the training database or ii) the values of the topographic factors of the restoration site are beyond their ecological ranges (e.g. if the elevation of the restoration site is 250 m and a species as an elevation range bounded between 1000 and 3000 m, such a species cannot be modeled).

## How to use *ResNatSeed*

*ResNatSeed* can be used both in R environment and through a ShinyApp. More information is available in the "Package installation and ShinyApp" vignette.

*ResNatSeed* can operate in two different ways depending on the source of the training database (i.e. the default or customized one):

-   The **DEFAULT** **training database** is based on vegetation data collected in the Piedmont Region (North Western Italy). See the vignette **TUTORIAL 1 - Default training database** for operational details.

-   The **CUSTOMIZED** **training database** can be based on any vegetation database belonging to any geographical area. See the vignette **TUTORIAL 2 - Customized training database** for operational details.

## 
