---
title: "Introduction to ResNatSeed"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_to_ResNatSeed}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ResNatSeed)
```

# Cosa fa

Calcoli basati su datset Piemonte, se si opera in altre aree geografiche si può 
selezionare un database ad hoc (vedi definizione **training database** nel paragrafo successivo)

# parole chiave

**vegetation and topographical variables database**: dataframe containing the composition of a set of vegetation surveys and their corresponding topographic variables (elevation, slope and aspect)

**training database**: dataframe with the species eligible for the statistical modelling, selected on the basis of their frequency and abundance in the **vegetation and topographical variables database**. To each species are associated the values of topographic variables (elevation, slope and aspect).

**species codes - CEP names**: 

**seed mixture and donor grassland composition**:

**Suitability Index (SI)**: suitability of a seed mixture or donor grassland to restore a site with specific topographic characteristics. It ranges between 0 and 1. When SI=0 the restoration site is totally beyond the optimal ecological ranges of all species of the seed mixture or donor grassland, which is therefore not appropriate for the site restoration. Conversely, when SI=1 the restoration site has the optimal ecological conditions for all species of the seed mixture or donor grassland, which is therefore perfectly appropriate for the site restoration.

**Reliability Index (RI)**: 

# Come si usa

L'utilizzo di ResNatSeed segue due procedimenti diversi a seconda che si utilizzi il training database di default (i.e. Piemonte) oppure uno specificato dall'utente. 

* **DEFAULT** training database ==> see the vignette **TUTORIAL 1 - Default training database**

* **CUSTOMIZED** training database  ==> see the vignette **TUTORIAL 2 - Customized training database**
