---
title: "TUTORIAL 2 -Customized training database"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TUTORIAL_2_-_Customized_training_database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
#system.file("extdata", package = "ResNatSeed")
load("~/Pacchetti R/ResNatSeed/inst/extdata/veg.composition.example.RData")
library(tidyr)
```

```{r setup}
library(ResNatSeed)
```

If the study area is beyond the Piedmont Region (North-Western Italy), it is advisable to provide a customized training database through the *trainingDB* function before using the *RestInd* function. 

In order to be processed with the *trainingDB* function, the **vegetation and topographical variables database** must be structured as follows (see Table 1 for an example):

* Rows of the dataframe are the surveys
* The first column reports the survey codes
* The second, third and fourth columns report the topographical variables, respectively:
  * **Elevation** expressed in meters above sea level (m a.s.l.)
  * **Slope** expressed in degrees (°)
  * **Aspect** expressed in degrees from North (°N) as it will be converted to "southness" to avoid circular variable issues in the models run with *RestInd* (Chang et al., 2004)
* From the fifth column onwards, the plant species names. Plant species names do not necessarily have to be coded, they can be left in full. Afterwards, abbreviation codes will be automatically created in CEP names format: an abbreviation of species names according to the Cornell Ecology Programs (CEP), which uses eight-letter abbreviations for species. The CEP names code will be used to formulate the seed mixture or donor grassland composition.

Table 1. Example of the structure of the *vegetation and topographical variables database* to provide in the function *trainingDB*. This database includes 703 vegetation surveys and 532 plant species
```{r echo=FALSE}
veg.composition.example
```

At this point, the customized training database can be generated by specifying the name of the *vegetation and topographical variables database* in the *data* argument of the **trainingDB** function. 
Through this function it is possible to select the species eligible for the statistical modeling through two arguments:

* **spe.freq**: this argument allows to set a threshold of minimum frequency of each species in the surveys. It is advisable to set values greater than or equal to 30 to allow appropriate statistical modeling.

* **min.spe.abundance**: this argument allows to set a threshold of minimum abundance (greater than) of each species in each survey. When NULL the parameter is set to 0.


```{r}
training.custom<-trainingDB(data=veg.composition.example,
           spe.freq = 30,# only species occurring at least in 30 surveys will be retained
           min.spe.abundance = 1# only species with at least 1% of relative abundance will be retained
           )

```

Through **trainingDB** function, two dataframes are created and stored in a list, named in this example as 'training.custom'. The two dataframes are:

* **cep.names**: dataframe with the list of species suitable for modeling and their species codes (CEP names) to be used for the seed mixture or donor grassland composition. In this example 65 species (out of 532) are eligible for modeling 

```{r}
training.custom$cep.names
```

* **trainingDB.ResNatSeed**: training database to use in the 'RestInd' function

```{r}
head(training.custom$trainingDB.ResNatSeed)
```

From the list of species in 'training.custom$cep.names', it is necessary to create a database containing the seed mixture or donor grassland composition. The seed mixture or donor grassland composition must be a dataframe with two columns:

* First column: species code abbreviated in CEP names format
* Second column: abundance of each species. Abundance must be a number bounded between 0 and 100,  which can be either a species relative abundance or a species cover (sensu Pittarello 2016, Verdinelli 2022).

In this example, the donor grassland composition is characterized by four species: 

* Dactylis glomerata (CEP name: Dactglom), abundance: 25%
* Festuca ovina aggr. (CEP name: Festaggr), abundance: 35%
* Thymus serpyllum aggr. (CEP name: Thymaggr), abundance: 15%
* Lotus corniculatus (CEP name: Lotucorn), abundance: 8%

Total abundances amount to 83%. The total abundance of the seed mixture or donor grassland composition should not necessarily amount 100%. 

We can generate the dataframe of the donor grassland composition:

```{r}
donor.composition<-data.frame(
  species=c("Dactglom","Festaggr","Thymaggr","Lotucorn"),
  abundance=c(25,35,15,8)
)

donor.composition
```


It is now possible to use the *RestInd* function to calculate the Suitability Index (SI) and Reliability Index (RI) by means of the donor grassland composition (dataframe 'donor.composition') and of the elevation, slope, and aspect of restoration site:

* elevation: 1600 m a.s.l.
* slope: 10°
* aspect: 110° N

Remember that in the 'trainingDB' argument it must be specified the one created above, i.e. training.custom$trainingDB.ResNatSeed

```{r echo=TRUE}
RestInd(trainingDB = training.custom$trainingDB.ResNatSeed, 
        composition=donor.composition,  
        elevation=1600, 
        slope=10, 
        aspect=110
        )
```
  


## References

* Chang, C., P. Lee, M. Bai, and T. Lin. 2004. Predicting the geographical distribution of plant communities in complex terrain–a case study in Fushian Experimental Forest, north- eastern Taiwan. Ecography. 27:577–588. doi:10.1111/j.0906- 7590.2004.03852.x

* Pittarello, M., Probo, M., Lonati, M., Lombardi, G., 2016. Restoration of sub-alpine shrub-encroached grasslands through pastoral practices: effects on vegetation structure and botanical composition. Appl Veg Sci 19, 381–390. https://doi.org/10.1111/avsc.12222

* Verdinelli, M., Pittarello, M., Caria, M.C., Piga, G., Roggero, P.P., Marrosu, G.M., Arrizza, S., Fadda, M.L., Lombardi, G., Lonati, M., Nota, G., Sitzia, M., Bagella, S., 2022. Congruent responses of vascular plant and ant communities to pastoral land-use abandonment in mountain areas throughout different biogeographic regions. Ecol Process 11, 35. https://doi.org/10.1186/s13717-022-00379-9

