---
title: "TUTORIAL 1 - Default training database"
author: "Marco Pittarello and Davide Barberis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TUTORIAL_1_-_Default_training_database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ResNatSeed)
```

When the user uses default settings, the training database refers to the vegetation surveys from the Piedmont Region - North-Western Italy, which includes 258 plant species eligible to modeling. Such a list can be extracted through the command `data("cep.piem")`. Species names follow the Flora Alpina nomenclature [@aeschimann2004] and they are associated with the 'cep.names' code, an eight-letter abbreviation of species names according to the Cornell Ecology Programs (CEP).

```{r echo=TRUE}
data("cep.piem")

head(cep.piem)

```

From this list is possible to create the mixture or donor grassland composition database, which is characterized by two columns:

-   **First column**: species code abbreviated in CEP names format
-   **Second column**: abundance of each species. Abundance must be a number bounded between 0 and 100, which can be either a species relative abundance or a species cover (*sensu* [@pittarello2016]; [@verdinelli2022]).

In this example, the donor grassland composition is characterized by five species:

-   *Bromus erectus* (CEP name: Bromere), relative abundance: 25%
-   *Brachypodium rupestre* (CEP name: Bracrupe), relative abundance: 18%
-   *Festuca ovina* aggr. (CEP name: Festaggr), relative abundance: 22%
-   *Knautia arvensis* (CEP name: Knauarve), relative abundance: 8%
-   *Silene vulgaris* (CEP name: Silevulg), relative abundance: 5%

Total abundances amount to 78%. The total abundance of the seed mixture or donor grassland composition should not necessarily amount 100%.

We can generate the dataframe of the donor grassland composition:

```{r}
donor.composition<-data.frame(
  species=c("Bromere","Bracrupe","Festaggr","Knauarve","Silevulg"),
  abundance=c(25,18,22,8,5)
)

donor.composition
```

It is now possible to use the *`RestInd`* function to calculate the **Suitability Index (SI)** and **Reliability Index (RI)** by means of the donor grassland composition (dataframe 'donor.composition') and of the elevation, slope, and aspect of restoration site:

-   elevation: 2300 m a.s.l
-   slope: 15°
-   aspect: 135° N

```{r echo=TRUE}
RestInd(trainingDB = NULL, 
        composition=donor.composition,  
        elevation=2300, 
        slope=15, 
        aspect=135
        )
```

## References
